\bf Faster Neural Machine Translation Inference

### 2018-02-22 fast-beam/fast-beam-short.tex
fast

\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{batch-size.png}} 
\end{tabular}
\caption{Actual batch size during decoding (Europarl test set)}
\label{fig:batch-size}
\end{figure}

@@

The output layer of most deep learning models consist of the following steps
\begin{enumerate}
   \item \vspace{-3 mm} multiplication of the weight matrix with the input vector $p = w x$
   \item \vspace{-3 mm} addition of a bias term to the resulting scores $p = p + b$
   \item \vspace{-3 mm} applying the activation function, most commonly softmax $ p_i = \exp(p_i) / \sum \exp(p_i) $
   \item \vspace{-3 mm} a beam search for the best (or n-best) output classes $\argmax_i p_i$
\end{enumerate}
In models with a small number of classes such as binary classification, the computational effort required is trivial and fast but this is not the case for the large number of classes found in typical NMT models.

@@

\begin{algorithm}
\begin{algorithmic}

@@

Secondly, we are only interested in the probabilities of the best classes. Since they are now known at the start of the kernel, we compute softmax only for those classes. The outline of the our function is shown in Algorithm~\ref{algo:Fused Kernel}.

\begin{algorithm}
\begin{algorithmic}
\Procedure{Fused-Kernel}{vector $p$, bias vector $b$}

@@

The standard mini-batching algorithm, Algorithm~\ref{algo:Mini-batching}, encode the sentences for a batch, followed by decoding the batch. Decoding stop only once all sentences in the batch are completed.

\begin{algorithm}
\begin{algorithmic}
\Procedure{Mini-Batching}{}
\While{more input} 
  \State Create batch $b$
  \State Encode($b$)
  \While{batch is not empty} 
    \State Decode($b$)
    \ForAll{sentence $s$ in $b$}
      \If{trans($s$) is complete}
        \State Remove $s$ from $b$
      \EndIf
    \EndFor
  \EndWhile
\EndWhile

\end{algorithmic}
\caption{Mini-batching}
\label{algo:Mini-batching}
\end{algorithm}

Our proposal focuses on decoding as this is the more compute-intensive task, encoding and decoding asynchronously. The encoding step, Algorithm~\ref{algo:Encoding for top-up batching}, is similar to the main loop of the standard algorithm but the results are added to a queue to be consumed by the decoding step.

\begin{algorithm}
\begin{algorithmic}

@@

Rather than decoding a batch until completion, new sentences are added to the batch as old sentences completes, Algorithm~\ref{algo:Decoding for top-up batching}.

\begin{algorithm}
\begin{algorithmic}

@@

For inference, we used and extend Amun~\citep{junczys2016neural}, the fastest open-source inference engine we are aware of for the model used in this paper. We used a beam size of 5, mini-batch of 128 sentences and maxi-batch 1280, unless otherwise stated.

@@

We trained a German-English with data from the Europarl corpus~\citep{Koehn:2005:MTS}, our test set consisted of a subset of the Open-Subtitles corpus, Table~\ref{tab:corpora}.

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		 & OpenSubtitles \\ \hline
\# sentences  	 & 50,000 \\
\# sub-words 	 & 467,654 \\ 
Avg sub-words/sent & 9.4 \\
Std dev subwords/sent & 6.1 \\ \hline
\end{tabular}
\end{center}
\caption{Test sets}
\label{tab:corpora}
\end{table}

@@

\section{Conclusion and Future Work}

We have presented two methods for faster deep-learning inference, targeted at neural machine translation.

The first method focused on output layer of the neural network which accounts for a large part of the running time of the NMT model. By fusing the output layer with the beam search, we are able to increase translation speed by up to 41\%.

The second method replaces the mini-batching algorithm with one that avoids decoding with a small number of sentences, maximizing the parallel processing potential of GPUs. For certain scenarios, this increases translating  speed by up to 12\%.

For future work, we would like to apply our optimization for other NLP and deep-learning tasks. We are also interested in further optimization of the output layer in NMT, specifically the matrix multiplication which still takes up a significant proportion of the translation time.

>>>>

\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{batch-size.png}} 
\end{tabular}
\caption{Actual batch size during decoding}
\label{fig:batch-size}
\end{figure}

@@

The output layer of most deep learning models consist of the following steps
\begin{enumerate}
   \item \vspace{-3 mm} multiplication of the weight matrix with the input vector $p = w x$
   \item \vspace{-3 mm} addition of a bias term to the resulting scores $p = p + b$
   \item \vspace{-3 mm} applying the activation function, most commonly softmax $ p_i = \exp(p_i) / \sum \exp(p_i) $
   \item \vspace{-3 mm} a beam search for the best (or n-best) output classes $\argmax_i p_i$
\end{enumerate}

@@

\begin{algorithm}
\begin{algorithmic}
\small

@@

Secondly, we are only interested in the probabilities of the best classes. Since they are now known at the start of the kernel, we compute softmax only for those classes. The outline of the our kernel is shown in Algorithm~\ref{algo:Fused Kernel}.

\begin{algorithm}
\begin{algorithmic}
\small

\Procedure{Fused-Kernel}{vector $p$, bias vector $b$}

@@

The standard mini-batching algorithm encode the sentences for a batch, followed by decoding the batch. Decoding stop only once all sentences in the batch are completed.

\begin{algorithm}
\begin{algorithmic}
\small

@@

Our proposal focuses on decoding as this is the more compute-intensive task, encoding and decoding asynchronously. The encoding step, Algorithm~\ref{algo:Encoding for top-up batching}, is similar to that in mini-batching except that the results are added to a queue.

The decoding continuously process the same batch, adding new sentences as old sentences completes, Algorithm~\ref{algo:Decoding for top-up batching}.

\begin{algorithm}
\begin{algorithmic}
\small

@@

For inference, we used and extend Amun~\citep{junczys2016neural}. We used a beam size of 5, mini-batch of 128 sentences and maxi-batch 1280, unless otherwise stated.

@@

The German-English version of the Europarl corpus~\citep{Koehn:2005:MTS} was used to train the model, our test set consisted of the first 50,000 sentences of the Open-Subtitles corpus~\citep{TIEDEMANN12.463}.

@@
